Study sample characteristics in chronobiology and sleep research

### 2021-05-19 article.Rmd
Updates

author: 
  - name          : "Selma Tir"
    affiliation   : "1,2"
    email         : "selma.tir@ndcn.ox.ac.uk"
    role:
      - Data curation
      - Investigation
      - Software
      - Visualization
      - Writing – original draft
      - Writing – review & editing
  - name          : "Rhiannon White"
    affiliation   : "1,3"
    email         : "r.white.5@warwick.ac.uk"
    role:         
      - Investigation
      - Writing – original draft
      - Writing – review & editing
  - name          : "Manuel Spitschan"
    affiliation   : "1,4,5"
    corresponding : yes    # Define only one corresponding author
    email         : "manuel.spitschan@psy.ox.ac.uk"
    role:
      - Conceptualization
      - Data curation
      - Funding acquisition
      - Investigation
      - Methodology
      - Project administration
      - Software
      - Writing – original draft
      - Writing – review & editing

@@

documentclass     : "apa6"
classoption       : "jou"
output            : papaja::apa6_pdf
---

>>>>

author: 
  - name          : "Selma Tir"
    affiliation   : "1,2"
    email         : "selma.tir@ndcn.ox.ac.uk"
    role:
      - Data curation
      - Investigation
      - Software
      - Visualization
      - Writing – original draft
      - Writing – review & editing
  - name          : "Rhiannon White"
    affiliation   : "1,3"
    email         : "r.white.5@warwick.ac.uk"
    role:         
      - Investigation
      - Writing – original draft
      - Writing – review & editing
  - name          : "Manuel Spitschan"
    affiliation   : "1,4,5"
    corresponding : yes    # Define only one corresponding author
    email         : "manuel.spitschan@psy.ox.ac.uk"
    address       : Department of Experimental Psychology, University of Oxford, Anna Watts Building, Radcliffe Observatory Quarter, Woodstock Rd, Oxford, OX2 6GG, United Kingdom
    role:
      - Conceptualization
      - Data curation
      - Funding acquisition
      - Investigation
      - Methodology
      - Project administration
      - Software
      - Writing – original draft
      - Writing – review & editing

@@

documentclass     : "apa6"
classoption       : "jou"
output            : papaja::apa6_docx
---
